In the Crucible: Massive Compact Galaxies with High-Velocity Outflows and Eddington-Limited Star Formation

### 2012-04-18 trunk/tex/sigmasfr/ms.tex
revisions to section 3.1

While the SEDs (see Figure~\ref{fig:seds}) and optical spectra (see
Figure~\ref{fig:spectra}) for our sample indicate that their
bolometric output is dominated by star formation, it is worthwhile to
consider the amount of ongoing AGN activity in these systems.  The
strongest case for detectable AGN emission among the high-$\sigmasfr$
galaxies can be made for J1506+5402, which has a weak
\nev~$\lambda3426$ emission line typically associated with AGN
activity \citep[e.g., ][]{abe08}.  This galaxy was observed with the
Chandra X-ray Observatory (proposal ID 11700896, PI: C. Tremonti) and
had four detected counts, corresponding to a 0.5--8.0~keV X-ray
luminosity of $10^{42.7}$~erg~s$^{-1}$ (see P. Sell et al., in
preparation for more details on the 12/29 galaxies with Chandra
observations).  Using the relationship between 2--10~keV X-ray and
12.3~$\mu$m mid-IR luminosity for AGNs from \citet{gan09}, one would
expect a source with
$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{42}$~erg~s$^{-1}$ to
have
$L_{\textnormal{\scriptsize{MIR}}}\approx7\times10^{42}$~erg~s$^{-1}$,
which is 400$\times$ smaller than observed luminosity for J1506+5402,
$L_{\textnormal{\scriptsize{MIR}}}\approx3\times10^{45}$~erg~s$^{-1}$.
If this source were Compton-thick \citep[e.g., the typical 2--10~keV
  attenuation for local Compton-thick AGNs is a factor of
  100;][]{dia09}, then the expected mid-IR AGN contribution could be
relevant at the $\lesssim$30\% level, but this would not affect our
conclusions that this galaxy is starburst dominated with a $\sigmasfr$
value near the Eddington limit.  As is the case for typical ULIRGs
\citep[e.g.,][]{far07}, there is certainly evidence for AGN activity
in a fraction of our sample, but the bolometric output is dominated by
star formation.

@@

@@

>>>>

While the SEDs (Figure~\ref{fig:seds}) and optical spectra
(Figure~\ref{fig:spectra}) for our sample indicate that their
bolometric output is dominated by star formation, it is worthwhile to
consider the level of ongoing AGN activity and its effect on our
measurements.  Among the high-$\sigmasfr$ galaxies, the strongest case
for detectable AGN emission can be made for J1506+5402, which has the
most luminous \oiii~$\lambda5007$ line among the 29 galaxies observed
by HST.  This source also has a weak \nev~$\lambda3426$ emission line,
which is associated with AGN activity \citep[e.g.,][]{abe08,gil10}.
It was observed with the Chandra X-ray Observatory (proposal ID
11700896, PI: C. Tremonti) and had four detected counts, corresponding
to a 0.5--8.0~keV X-ray luminosity of $10^{42.7}$~erg~s$^{-1}$ (see
P. Sell et al., in preparation for more details on the 12/29 galaxies
with Chandra observations).  Using the relationship between 2--10~keV
X-ray and 12.3~$\mu$m mid-IR luminosity for AGNs from \citet{gan09},
one would expect a source with
$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{42}$~erg~s$^{-1}$ to
have
$L_{\textnormal{\scriptsize{MIR}}}\approx7\times10^{42}$~erg~s$^{-1}$,
which is 400$\times$ smaller than observed luminosity for J1506+5402
($L_{\textnormal{\scriptsize{MIR}}}\approx3\times10^{45}$~erg~s$^{-1}$).
Based on its \oiii\ luminosity ($10^{42.1}$~erg~s$^{-1}$, a
significant fraction of which could be attributed to star formation)
and the calibration for type 1 AGNs from \citet{hec05}, one would
expect an intrinsic 2--10~keV luminosity of
$L_{\textnormal{\scriptsize{X}}}\approx5\times10^{43}$~erg~s$^{-1}$,
suggesting absorption by a factor of $\sim10$ in the X-rays.  However,
even if the X-ray attenuation were a factor of 100, which is the
typical value for local Compton-thick AGNs \citep{dia09}, the expected
mid-IR AGN contribution would only be relevant at the $\lesssim$30\%
level.  Similar to local ULIRGs \citep[e.g.,][]{far07}, the bolometric
output of the galaxies in our sample is dominated by star formation,
and our conclusions regarding large $\sigmasfr$ values are not
affected by AGN contamination.

% ased on its \oiii\ luminosity $L(\oiii)=10^{42.1}$~erg~s$^{-1}$, the
% expected X-ray luminosity \citep[adopting the relationship between
%   \oiii\ and X-ray luminosity for type 1 AGNs from][]{hec05}

@@

\bibitem[Gilli et al.(2010)]{gil10} Gilli, R., Vignali, C., Mignoli,
  M., et al.\ 2010, \aap, 519, A92

@@

\bibitem[Heckman et al.(2005)]{hec05} Heckman, T.~M., Ptak, A.,
  Hornschemeier, A., \& Kauffmann, G.\ 2005, \apj, 634, 161
